Hydra Battles and Cie

### 2021-02-24 doc/part-hydras.tex
restructuring some .v files
minor corrections

We express this number in terms of the Hardy hierarchy of fast-growing 
functions~\cite{BW85, Wainer1970, KS81, Promel2013}.
 From the \coq{} user's point of view, such  functions are  very 
attractive:  they are defined as functions  in \gallina{}, and we can apply them \emph{in theory}, but they are so complex that you will never be able to look at the result of the computation.
 Thus, our knowledge on these functions must rely on \emph{proofs}. In our development, we use often the rewriting rules generated by \coq's \texttt{Equations} plug-in.

@@

\begin{definition}
Let $0<\alpha<\epsilon_0$ be any ordinal, and $s$ a sequence of strictly positive natural numbers. 
We say that $s$ is \emph{minimally $\alpha$-large} (in short:
\emph{$\alpha$-mlarge}) if $s$ if $s$ is $\alpha$-large 
 and every strict prefix of $s$ leads to a non-zero ordinal (\emph{cf} Sect.~\vref{sect:path-to-def}).

@@

@@

They also consider large (but not minimally large) sets. They can be defined in
\coq{} as follows:

Definition large alpha (s:list nat) := gnaw alpha s = zero.
\end{Coqsrc}
\end{remark}

@@

\begin{Coqsrc}
Lemma LF1 : forall n,  F_ 1 n = S (2 * n).

@@

>>>>

We express this number in terms of the Hardy hierarchy of fast-growing 
functions~\cite{BW85, Wainer1970, KS81, Promel2013}.
 From the \coq{} user's point of view, such  functions are  very 
attractive:  they are defined as functions  in \gallina{}, and we can apply them \emph{in theory}, but they are so complex that you will never be able to look at the result of the computation.
 Thus, our knowledge on these functions must rely on \emph{proofs}, not tests. In our development, we use often the rewriting rules generated by \coq's \texttt{Equations} plug-in.

@@

\begin{definition}
Let $0<\alpha<\epsilon_0$ be any ordinal, and $s$ a finite sequence $\langle s_1, s_2, \dots, s_N\rangle$ of strictly positive natural numbers.

We say that $s$ is \emph{$\alpha$-large} if the sequence $\langle \alpha_0=\alpha,\dots,\alpha_{i+1}=\canonseq{\alpha_i}{i+1},\dots \rangle$ leads to $0$.

We say that $s$ is \emph{minimally $\alpha$-large} (in short:
\emph{$\alpha$-mlarge}) if $s$ is $\alpha$-large 
 and every strict prefix of $s$ leads to a non-zero ordinal (\emph{cf} Sect.~\vref{sect:path-to-def}).

@@

Definition large alpha (s:list nat) := gnaw alpha s = zero.
\end{Coqsrc}

@@

@@

\begin{Coqsrc}
Lemma LF1 : forall i,  F_ 1 i = S (2 * i).

@@

\begin{exercise}
Prove the following property:

\begin{Coqsrc}
Lemma LF3 : dominates_from  2 (F_ 3) (fun  n => iterate exp2 n n).
\end{Coqsrc}
\end{exercise}
